---
title: "Definitions af sygdom, procedure, mecdicin og outcomes i HjerteTal2"
output:
  pdf_document: default
  html_document:
    df_print: paged
---
```{r intro, include=FALSE, echo = FALSE}
library(officer)
library(flextable)
invisible(source(file = "PrepDefinitions.R"))
```

Diagnoses, procedures, and medications are coded based on the Danish Sygehusvæsnets Klassifikationssystem (SKS) as of 2018-10-15. 

### Illnesses/outcomes

The illnesses/outcomes used in HjerteTal are based on the ICD-10 codes as follows:

```{r, echo = FALSE, cache = TRUE}

diag_pretty <- lapply(diag_list, function(i) i[1, .(desc_dk, desc_en, code_simple, duration, diag_type, pat_type)]) %>%
  rbindlist()

out_pretty <- flextable(diag_pretty, col_keys = c("desc_en", "code_simple", "duration", "diag_type", "pat_type")) %>%
  width(j = c("desc_en"), width = 2.5) %>%
  width(j = "code_simple", width = 3.0) %>%
  width(j = "duration", width = 1) %>%
  height_all(height = 0.55) %>%
  align(j = c("desc_en", "code_simple", "duration", "diag_type", "pat_type")) %>%
  align(part = "header") %>%
  fontsize(size = 14) %>%
  fontsize(size = 16, part = "header") %>%
  bold(part = "header") %>%
  set_header_labels(desc_en = "Sygdomme",
                    code_simple = "ICD-10 code(s)",
                    duration = "Duration after diagnosis",
                    diag_type = "Diagnosis type",
                    pat_type = "Patient type")

out_pretty

```

    
<br><br>
        
#### Procedures

The following codes were used to classify operations and procedures

```{r, echo = FALSE, cache = TRUE}
opr_pretty <- lapply(opr_list, function(i) i[1, .(desc_dk, desc_en, code_simple)]) %>%
  rbindlist()

out_pretty <- flextable(opr_pretty, col_keys = c("desc_en", "code_simple")) %>%
  width(j = c("desc_en"), width = 2.1) %>%
  width(j = "code_simple", width = 4.5) %>%
  height_all(height = 0.59) %>%
  align(j = c("desc_en", "code_simple")) %>%
  align(part = "header") %>%
  fontsize(size = 14) %>%
  fontsize(size = 16, part = "header") %>%
  bold(part = "header") %>%
  set_header_labels(desc_en = "Procedure",
                    code_simple = "SKS codes")

out_pretty
```
<br><br>

#### Medications

The following codes were used to classify medications
```{r, echo = FALSE, cache = TRUE}
med_pretty <- lapply(med_list, function(i) i[1, .(desc_dk, desc_en, code_simple)]) %>%
  rbindlist()

out_pretty <- flextable(med_pretty, col_keys = c("desc_en", "code_simple")) %>%
  width(j = c("desc_en"), width = 2.1) %>%
  width(j = "code_simple", width = 4.5) %>%
  height_all(height = 0.59) %>%
  align(j = c("desc_en", "code_simple")) %>%
  align(part = "header") %>%
  fontsize(size = 14) %>%
  fontsize(size = 16, part = "header") %>%
  bold(part = "header") %>%
  set_header_labels(desc_en = "Medication type",
                    code_simple = "SKS codes")
out_pretty

```

#### Rates and standardizations
We used the European Standard population, 2013, taken from:
http://www.isdscotland.org/Products-and-Services/GPD-Support/Population/Standard-Populations/


